\textsf{Are large language models superhuman chemists?}

### 2024-10-19 src/tex/sections/manually_sources_table.tex
more additions

Chemistry olympiad & National and International Olympiads held in US, UK and Moldova && \variable{output/question_count_per_dir/json_file_counts_icho.txt} \\

@@

>>>>

Chemistry olympiad & National and International Olympiads held in US, UK, Romania and Moldova && \variable{output/question_count_per_dir/json_file_counts_icho.txt} \\

@@

\midrule Inorganic Chemistry & Based on questions from the national examination of the Russian Federation && 3\\
